---
title: "BA810 individual assignement"
author: "Qiaoling Huang (U20421641)"
date: "10/5/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup
```{r}
install.packages("glmnet")
library(tidyverse)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(glmnet)
theme_set(theme_bw())
```
## Load the CA housing Dataset
```{r}
getwd()
dd <- read_csv("../housing.csv")
glimpse(dd)
```

The total_bedrooms column has missing data that we are going to impute.
```{r}
total_bedrooms_median <- median(dd$total_bedrooms, na.rm = TRUE)
dd <- dd %>%
replace_na(list("total_bedrooms" = total_bedrooms_median))
dd
```

Split dataset in train and test.
```{r}
# use this piece of code as is
train_offsets <- seq(5000)
test_offsets <- 15000 + seq(3000)
x_data <- model.matrix( ~ -1 + total_rooms + total_bedrooms +
households + housing_median_age +
population + median_income + ocean_proximity, dd)
# outcome is median house value in millions
y_data <- dd$median_house_value / 1e6
x_train <- x_data[train_offsets, ]
y_train <- y_data[train_offsets]
x_test <- x_data[test_offsets, ]
y_test <- y_data[test_offsets]
```

## Run Lasso regression
```{r}
est <- glmnet(x_train, y_train, alpha = 1, nlambda = 100)
est$lambda
plot(est)
```

Next, we will use each of these 100 models to create predictions for both train and test.
```{r}
y_train_hat<- predict(est, s = est$lambda, newx = x_train)
y_test_hat <- predict(est, s = est$lambda, newx = x_test)

mse_train=vector()
mse_test=vector()
for (i in 1:length(est$lambda)) {
  mse_train[i] <- mean((y_train - y_train_hat[,i])^2)
  mse_test[i] <- mean((y_test - y_test_hat[,i])^2)
}
mse_train
mse_test
plot(mse_train)
plot(mse_test)
```
Choose the lowest MSE for train and test
```{r}
lambda_min_mse_train <- est$lambda[which.min(mse_train)]
lambda_min_mse_test <- est$lambda[which.min(mse_test)]
lambda_min_mse_train
lambda_min_mse_test
```

## Aggregate all MSEs in a single dataset
Create a tibble of train MSEs and lambdas
```{r}
dd_mse <- tibble( 
  lambda = est$lambda,
  mse = mse_train,
  dataset = "Train"
)

dd_mse <- rbind(dd_mse, tibble(
  lambda = est$lambda,
  mse = mse_test,
  dataset = "Test"
))

dd_mse
```

## Plot the MSEs
```{r}
mins <- dd_mse %>% 
  group_by(dataset) %>% 
  filter(mse == min(mse))

dd_mse %>% 
  ggplot(aes(lambda, mse, color = dataset))+
  geom_line()+
  scale_x_reverse()+
   labs(color = "Dataset",
       x = "λ",
       y = "MSE")+
  geom_point(data = mins, aes(x = lambda, y = mse))+
  theme_classic()


```

## Discuss the results of the best fitting model
```{r}
print(lambda_min_mse_test)
coef(est, s = lambda_min_mse_test)
```

If I am considering investing in CA real estate, I will mainly focus on median_income, ocean_proximity<1H ocrean, and ocean_proximityINLAND as the coefficients shows these variables have significant correlation. Although total_bedrooms has correlation, but the coefficient is too small so I think there is no need to worry about.

## Collabration statement
I completed most of the assignment by myself based on reading the text book from page 251 to page 255. Meanwhile, Zhang Hang from cohort A taught me writing the code to create a vector contains 100 MSE. And Shangkun Zuo from cohort B taught me the coefficient part. 
